---
title: "MIB for Law Enforcement - Combined Sample - Methods"
author: "Dr. Calvin Lai"
date: "07/24/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
always_allow_html: yes
---

```{r setup, include = FALSE}
# Package names
packages <- c("sjPlot",  "psych", "foreign", "tidyverse", "glue", "effsize", "cowplot", "lme4", "lmerTest", "corrplot", "summarytools", "effsize", "ggstatsplot", "ggthemes")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))
rm(list = c("packages", "installed_packages"))

# Data to load 
t1t2 <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2.csv", guess_max = min(12000))
t1t2Long <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2_long.csv", guess_max = min(12000))
t1t2LongBiasworryT1 <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2_long_biasworryt1.csv", guess_max = min(12000))
t1t2LongKnowledgeT1 <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2_long_knowledget1.csv", guess_max = min(12000))
t1t2LongTheoriesT1 <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2_long_theoriest1.csv", guess_max = min(12000))
t1t2LongStratKnowT1 <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2_long_stratknowt1.csv", guess_max = min(12000))
t1t2LongStratEfficacyT1 <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2_long_stratefficacyt1.csv", guess_max = min(12000))
t1t2LongStratMotT1 <- read_csv("C:/Users/Calvin/Documents/Dropbox/Projects/mib/data/mib_combined_t1t2_long_stratmott1.csv", guess_max = min(12000))
```


### Participants, Combined Sample

Participants were sworn officers of a police department or departments within the United States who took part in a training session. We collected `r dim(t1t2)[1]` surveys who completed Time 1 and Time 2.

Participants had worked an average of `r round(mean(t1t2$yearsworked, na.rm=T), 0)` years in the department, with `r round((prop.table(table(t1t2$yearsworked_5y))[2]) * 100, 0)`% having worked in the department for 5 years or more. `r round(prop.table(table(t1t2$rank))[1] * 100, 0)`% of participants were below Sergeant rank, `r round(prop.table(table(t1t2$gender_d))[2] * 100, 0)`% were male, and `r round(prop.table(table(t1t2$education_ba))[2] * 100, 0)`% had a bachelor's degree or higher. Of the `r round(prop.table(table(is.na(t1t2$race)))[1] * 100, 0)`% of participants that reported their race, `r round((prop.table(table(t1t2$race))[5]) * 100, 0)`% were White, `r round((prop.table(table(t1t2$race))[2]) * 100, 0)`% were Black, `r round((prop.table(table(t1t2$race))[3]) * 100, 0)`% were Hispanic/Latino, `r round((prop.table(table(t1t2$race))[1]) * 100, 0)`% were Asian, and `r round((prop.table(table(t1t2$race))[4]) * 100, 0)`% were multi-racial.

```{r intergroup contact, echo=F, warning=F, message=F}
freq(t1t2$frequency_white)
freq(t1t2$frequency_black)
freq(t1t2$frequency_hispanic)
freq(t1t2$frequency_asian)
freq(t1t2$frequency_trans)
freq(t1t2$frequency_gay)
```

### Reliability analyses
```{r reliability analyses, echo=F, warning=F, message=F}
# Time 1
psych::alpha(t1t2 %>% select(knowledge_bias.t1, knowledge_race.t1, knowledge_culture.t1))$total$raw_alpha
psych::alpha(t1t2 %>% select(theories1.t1, theories2.t1))$total$raw_alpha
psych::alpha(t1t2 %>% select(biasworry_black.t1, biasworry_asian.t1, biasworry_hispanic.t1, biasworry_lgb.t1, biasworry_trans.t1))$total$raw_alpha
psych::alpha(t1t2 %>% select(substitution_use, perspective_use, exposure_use, individuation_use, mindful_use))$total$raw_alpha

psych::alpha(t1t2 %>% select(centrality1, centrality2, centrality3))$total$raw_alpha
psych::alpha(t1t2 %>% select(respect1, respect2, respect3, respect4))$total$raw_alpha

# Time 2
psych::alpha(t1t2 %>% select(knowledge_bias.t2, knowledge_race.t2, knowledge_culture.t2))$total$raw_alpha
psych::alpha(t1t2 %>% select(theories1.t2, theories2.t2))$total$raw_alpha
psych::alpha(t1t2 %>% select(biasworry_black.t2, biasworry_asian.t2, biasworry_hispanic.t2, biasworry_lgb.t2, biasworry_trans.t2))$total$raw_alpha
psych::alpha(t1t2 %>% select(substitution_intend, perspective_intend, exposure_intend, individuation_intend, mindful_intend))$total$raw_alpha

psych::alpha(t1t2 %>% select(strat_efficacy.t2, strat_know.t2, strat_mot.t2))$total$raw_alpha

# Time 3
psych::alpha(all %>% select(knowledge_bias.t3, knowledge_race.t3, knowledge_culture.t3))$total$raw_alpha
psych::alpha(all %>% select(theories1.t3, theories2.t3))$total$raw_alpha
psych::alpha(all %>% select(biasworry_black.t3, biasworry_asian.t3, biasworry_hispanic.t3, biasworry_lgb.t3, biasworry_trans.t3))$total$raw_alpha
psych::alpha(all %>% select(substitution_used, perspective_used, exposure_used, individuation_used, mindful_used))$total$raw_alpha

psych::alpha(all %>% select(strat_efficacy.t3, strat_know.t3, strat_mot.t3))$total$raw_alpha
```


```{r temp}
# NOTE: Cohen's d and t-tests were not used in reporting.
# Knowledge
t.test(t1t2$knowledge.t1, mu = 1)
sd(t1t2$knowledge.t1,na.rm=T)
effsize::cohen.d(t1t2$knowledge.t1, f = NA, mu =1, na.rm = T)
freq(t1t2$knowledge.t1)

# Concern
t.test(t1t2$biasworry.t1, mu = 1)
sd(t1t2$biasworry.t1,na.rm=T)
effsize::cohen.d(t1t2$biasworry.t1, f = NA, mu =1, na.rm = T)
freq(t1t2$biasworry.t1)

# Strategy Use
t.test(t1t2$strategy_use)
sd(t1t2$strategy_use,na.rm=T)
effsize::cohen.d(t1t2$strategy_use, f = NA, mu =0, na.rm = T)
freq(t1t2$strategy_use)

freq(t1t2$perspective_use)
freq(t1t2$mindful_use)
freq(t1t2$substitution_use)
freq(t1t2$exposure_use)
freq(t1t2$individuation_use)



# Internal survey calculations

# 1)	Whether the facilitators were knowledgeable, credible, and engaging on a scale from 1 (Strongly agree) to 7 (Strongly disagree). 
psych::m2t(1.35,1.70,.78,1.09,n1=3629,n2=2103) 
t2d(14.09422,n1=3629,n2=2103)

# 5)	Whether officers would use information from the workshop in their work or personal life on a scale from 1 (Strongly agree) to 7 (Strongly disagree). 
psych::m2t(1.95, 2.26,1.29,1.45,n1=3626,n2=2103) 
t2d(8.37,n1=3626,n2=2103)
```

```


### General perceptions of bias, Combined Sample
```{r Combined Sample  General perceptions of bias, echo=F, warning=F, message=F}
lmer.null <- summary(lmer(knowledge ~ (1|id), data = t1t2Long))

anova(lmer(knowledge ~ time + (1|id), data = t1t2Long), lmer.null)
summary(lmer(knowledge ~ time + (1|id), data = t1t2Long))
effsize::cohen.d(t1t2$knowledge.t2, t1t2$knowledge.t1, paired=T, na.rm = T)

summary(lmer(biasworry ~ time + (1|id), data = t1t2Long))
effsize::cohen.d(t1t2$biasworry.t2, t1t2$biasworry.t1, paired=T, na.rm = T)

summary(lmer(theories ~ time + (1|id), data = t1t2Long))
effsize::cohen.d(t1t2$theories.t2, t1t2$theories.t1, paired=T, na.rm = T)

```

### Strategies to manage bias, Combined Sample
```{r Combined Sample  strategies to manage bias, echo=F, warning=F, message=F}
# know
t.test(t1t2$strat_know.t2, mu = 1)
sd(t1t2$strat_know.t2,na.rm=T)
effsize::cohen.d(t1t2$strat_know.t2, f = NA, mu =1, na.rm = T)
freq(t1t2$strat_know.t2)

# Efficacy
t.test(t1t2$strat_efficacy.t2, mu = 1)
sd(t1t2$strat_efficacy.t2,na.rm=T)
effsize::cohen.d(t1t2$strat_efficacy.t2, f = NA, mu =1, na.rm = T)
freq(t1t2$strat_efficacy.t2)

# Motivation
t.test(t1t2$strat_mot.t2, mu = 1)
sd(t1t2$strat_mot.t2,na.rm=T)
effsize::cohen.d(t1t2$strat_mot.t2, f = NA, mu =1, na.rm = T)
freq(t1t2$strat_mot.t2)

# Strategy intentions
summary(lmer(strategy ~ time + (1|id), data = t1t2Long))
effsize::cohen.d(t1t2$strategy_intend, t1t2$strategy_use, paired=T, na.rm = T)
mean(t1t2$strategy_intend,na.rm=T)
```


